[Re] Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)

### 2020-02-16 analysis/paper.Rmd
updates to RMD to add a function and added metadaata.yaml

---
title: "[Re] Marriage and happiness: Oishi, Kesebir, and Diener (2011)"
author: "Lauren Heintz, Tara Wilson, Ben Mathieu, Will Wright"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: bookdown::word_document2
bibliography: bibliography.bibtex
link-citations: yes

@@

@@

# References

>>>>

---
title: "[Re] Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)"
author: "Lauren Heintz, Tara Wilson, Ben Mathieu, Will Wright"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: bookdown::word_document2
bibliography: bibliography.bibtex
link-citations: yes

@@

```{r, echo = FALSE}

myfunction <- function(arg1, arg2){
  print(seq(arg2))
  print("hello world")
}

myfunction(32,44)

```

@@

# References Cited
